---
title: "homework2"
author: "Yingtong Lyu"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Question 3.Write the R code to recreate the graph from the Activity 2 (Problem 4).

###3.1 load the lab2 data
```{r}
library(tidyverse)
lab2<-read.csv("C://Users/ColdSun/Documents/WCM/BDS/lab2.csv")
```
###3.2 tidy the data and summarize 
```{r}
temp <- lab2%>%
  gather(indexes=2:10,key=time_category,value=value)%>%
  separate(time_category,into=c("time","category"),sep = "_") %>%
  group_by(time,category)%>%
  summarise(mean=mean(value),sd=sd(value))
```
```{r}
temp$time<- c("base","base","base",
              "one year", "one year", "one year",
              "two years","two years","two years")
temp
```
###3.3 Plot 
```{r}
ggplot(temp,aes(x=time,y=mean,group=category,col=category))+
  geom_line(position=position_dodge(0.2))+
  geom_point(position=position_dodge(0.2))+
  geom_errorbar(aes(ymin=mean-sd,ymax=mean+sd),width=0.1,
                position=position_dodge(0.2),size=1)+
  scale_y_continuous(limits = c(0,100), breaks=seq(0,100,by=25))+
  labs(y = "Sample mean and standard deviation", x = "Time of report")+
  theme_bw()+
  theme(legend.position = c(0.93,0.2),legend.title = element_blank())
  
```
##Question 4.Download two files:
. coverage.csv - Health Insurance Coverage of the Total Population (2013 - 2016)
. expenditures.csv - Health Care Expenditures by State of Residence (in millions)
4.1 Make the data frames "tidy".
4.2 Merge two data frames: the resulting data frame should contain information about coverage and
expenditures for years 2013-2016. Please note that file expenditures.csv does not contain years
2015-2016.

###4.1 load data 
```{r}
coverage<-read.csv("C:/Users/ColdSun/Documents/WCM/BDS/coverage.csv", 
                   skip = 2, header = TRUE,nrows = 52,stringsAsFactors = F)
expenditures<-read.csv("C:/Users/ColdSun/Documents/WCM/BDS/expenditures.csv",
                       skip = 2, header = TRUE,nrows = 52,stringsAsFactors = F)
```

###4.2 tidy coverage data
```{r}
tidy_coverage<- coverage%>%
  gather(indexes= 2:ncol(coverage), key="XYear_Insurance",value="Amount")%>%
  separate(XYear_Insurance, into = c("XYear","Insurance"),sep = '__')%>%
  mutate(Year=gsub("X","",XYear))%>%
  select(Location,Year,Insurance,Amount)
head(tidy_coverage)
```
###4.3 tidy expenditures data
```{r}
tidy_expenditures<- expenditures%>%
  gather(indexes= 2:ncol(expenditures),
         key="XYear_Total.Health.Spending",value="Total_Spending")%>%
  separate(XYear_Total.Health.Spending, 
           into = c("XYear","Total.Health.Spending"),sep = '__')%>%
  mutate(Year=gsub("X","",XYear))%>%
  select(Location,Year,Total_Spending)
head(tidy_expenditures)
```
###4.4 merge two data and creat tidy data frame
```{r}
tidy<-merge(tidy_coverage, tidy_expenditures, by = c("Location", "Year"), all =TRUE) %>%
  filter(Year >= 2013 & Year <= 2016)
tidy
```
